### 2023-10-17 tex/article.tex
Last fixes
Fix now published references

  \vspace{\baselineskip}
  \foreignlanguage{french}{
    Soumis à \glshref{biogeosciences} le \frenchdate{2022}{12}{22}.\\
    Accepté après révisions mineures, et sous presse.\\
    Pre-print disponible sur EGUsphere (\textsc{doi}:~\href{\glsentryurl{preprint-bgs}}{\textsf{\glsentrydoi{preprint-bgs-doi}}}).
  }
}

@@

\begin{articleSubBlock}{Acknowledgments}
  CH benefited from a PhD scholarship by ENS.\@ The project was supported by TOSCA CNES and by the ENS CHANEL chair.
  We thank Daniele Iudicone, Francesco d'Ovidio, Sakina-Dorothée Ayata, and Amala Mahadevan for the useful discussions which helped to refine our methodology. We thank Xioa Liu for helping us reproduce their work.

>>>>

  \vspace{\baselineskip}
  \foreignlanguage{french}{
    Soumis à \glshref{biogeosciences} le \frenchdate{2022}{12}{22}.
    Publié le \frenchdate{2023}{5}{11}.
    La version finale soumise est reportée ci-après, sans les dernières corrections de l'éditeur.
    \textit{Biogeosciences} 20.9, p.~\numrange{1741}{1758}.
    \glsurl{haeck_2023}.
  }
}

@@

\begin{articleSubBlock}{Acknowledgments}
  CH benefited from a PhD scholarship by ENS.\@ The project was supported by TOSCA CNES and by the ENS CHANEL chair.
  We thank Daniele Iudicone, Francesco d'Ovidio, Sakina-Dorothée Ayata, and Amala Mahadevan for the useful discussions which helped to refine our methodology. We thank Xiao Liu for helping us reproduce their work.
